% \subsection{Functional Requirements}
The following functional requirements have been identified for the EasyTrip system.

F1: Travellers can find destinations with cheap flights when providing a departure city and dates.
    Goal-level requirement defining a key system function.
    
F2: Travellers should be able to provide a range of possible dates.
    Domain-level functionality supporting flexible searches.
    
F3: Travellers can have their device provide their current location.
    Domain-level feature leveraging geolocation services.
    
F4: Travellers can find cheap flights to a given destination.
    Domain requirement focusing on the flight search feature.
    
F5: Travellers can see a text list of cheap flights to a destination.
    Product-level requirement for displaying search results.
    
F6: Travellers can see prices for multiple tickets.
    Product-level requirement enabling comparison of ticket prices.

F7: Travellers can see destinations with cheap flights on a heatmap.
    Product-level feature enhancing visualization. See an example in figure 2.

F8: Travellers can change the dates for which the map shows data.
    Domain-level control for flight search customization.

F9: Travellers can see a text list of destinations with cheap flights.
    Product-level display of destinations based on search.

F10: Traveller can click through to ticket booking page for shown flights.
    Product-level requirement enabling ticket purchase.

F11: Travellers can select airports from the heatmap.
    Product-level feature allowing interactive selection.

F12: Travellers can find prices of multi-flight trips.
    Product-level requirement for multi-leg trip pricing.

F13: Travel agencies can find flights on behalf of clients.
    Goal-level requirement supporting B2B services.

F14: Travellers should be able to create accounts with email addresses and passwords.
    Product-level authentication requirement.

F15: The ownership of travellers' email addresses should be confirmed.
    Domain requirement ensuring valid accounts.

F16: Travellers should be able to change their email address.
    Product-level account management feature.

F17: Travellers should be able to change their passwords.
    Product-level security feature.

F18: Travellers should be able to reset their password if they have forgotten it.
    Product-level usability requirement.

F19: Travellers should be asked about receiving marketing emails.
    Domain-level requirement ensuring compliance with marketing preferences.

F20: A signed-in traveller can save favorite cities.
    Product-level feature for personalization.

F21: Product manager can request a statistics report.
    Goal-level requirement for system analytics.

F22: Marketer can have marketing email sent to relevant consenting travellers.
    Product-level marketing function.

% \subsection{Data dictionary}
% add a explanation and a table of the data dictionary
% Skriv en req on booking function, redirects. Från övning 5
% Lägg till IT Maintannce krav som att "De ska kunna använda systemet" för att få med alla stakeholders
