% In R4 only include features relevant mockups.

\begin{longtable}{|c|c|c|c|}
    \hline
\rowcolor{headergray}
\textbf{Release} & \textbf{Feature} & \textbf{Priority} & \textbf{Prioritization Motivation / Explanation} \\
\hline
\endfirsthead
\rowcolor{headergray}
\hline
\textbf{Release} & \textbf{Feature} & \textbf{Priority} & \textbf{Prioritization Motivation / Explanation} \\
\hline
\endhead
\hline
\endfoot
\hline
\endlastfoot

4 & Feature 1 & High & Explanation for Feature 1 \\
4 & Feature 2 & Medium & Explanation for Feature 2 \\
4 & Feature 3 & Low & Explanation for Feature 3 \\
\hline
5 & Feature 1 & High & Explanation for Feature 1 \\
5 & Feature 2 & Medium & Explanation for Feature 2 \\
5 & Feature 3 & Low & Explanation for Feature 3 \\
\hline

\end{longtable}

% Update ID of reqs
Release 4:
\begin{itemize}
    \item F8-D  Q8-D  The map should reflect date changes in under 2 seconds without requiring a full reload. See figure 2.
    \item F2-D  Q2-D  The system should support flexible date ranges spanning at least 30 days for price comparisons. See figure 2.
    \item F3-D  Q3-D  Location detection should be completed in under 3 seconds with at least 95\% accuracy.
    \item F4-D  Q4-P  The system should retrieve and display flight prices within 2 seconds for a standard query.
    \item F5-P  Q5-P  The list should support sorting by price, duration, and airline, with sorting applied in under 1 second.
    \item F7-P  Q7-D  The heatmap should update dynamically within 3 seconds of data input or changes.
    \item F8-D  Q8-D  The map should reflect date changes in under 2 seconds without requiring a full reload.
\end{itemize}

Release 5:
\begin{itemize}
    \item F15-D  Q15-D  Email verification links should be sent within 5 seconds and expire after 24 hours.
\end{itemize}
