\begin{enumerate}
    \item \textbf{Overall Validation}
    \begin{enumerate}
        \item Are the stakeholders goals and needs covered by the requirements?
        \item Are the business, domain, product and design level goals covered by the requirements?   
        \item Are the requirements justified?
        \item Are the requirements aligned with user and business needs?
        \item Are the system boundaries and requirements defined?
        \item Are the goals covered by the requirements?
        \item Are the requirements testable?
        \item Are the requirements complete?
        \item Are the requirements consistent?
        \item Are the requirements traceable?
        \item Are the requirements feasible?
        \item Are the requirements unambiguous?
        \item Are the requirements verifiable?
        \item Are the requirements clear and concise?
    \end{enumerate}
    \item \textbf{Quality Validation}
    \begin{enumerate}
        \item Does the requirements specifications cover performance?
        \item Does the requirements specifications cover usability?
        \item Does the requirements specifications cover safety and security?
        \item Does the requirements specifications cover reliability?
        \item Does the requirements specifications cover availability?
        \item Does the requirements specifications cover fault-tolerance?
        \item Does the requirements specifications cover maintainability?
        \item Does the requirements specifications cover portability?
        \item Does the requirements specifications cover scalability?
        \item Does the requirements specifications cover interoperability?
        \item Does the requirements specifications cover compliance?
        \item Does the requirements specifications cover privacy?
    \end{enumerate}
    \item \textbf{Special case Validation}
    \begin{enumerate}
        \item Does the requirements specifications cover data visualization?
        \item Does the requirements specifications cover data aggregation?
        \item Does the requirements specifications cover the heatmap of destinations with cheap flights?
        \item Does the requirements specifications cover the list of destinations with cheap flights?
    \end{enumerate}
\end{enumerate}